Einschätzung zu den Befindlichkeiten der Wirtschaft in den Nachbarländern

### 2022-10-30 Paper_neighbour_countries_NEW.Rmd
31.10.22

KOF_Baro_table %>% 
  gt(caption = "") %>%
  tab_header(title = md("KOF-Bartmeter. *Quelle:* KOF"),
             subtitle = "") %>% 
  fmt_date(
    columns = time,
    date_style = "month"
  ) %>% 
  fmt_number(
    columns = c(value, delta_vormonat),
    decimals = 1
  ) %>%
  cols_align(
    align = "left",
    columns = time
  ) %>% 
 text_transform(
    locations = cells_body(
      columns = delta_vormonat,
      rows = delta_vormonat > 0),
    fn = function(x) paste(x, md("\\textcolor{red}{\\FilledSmallTriangleUp}"))
  ) %>%
  text_transform(
    locations = cells_body(
      columns = delta_vormonat,
      rows = delta_vormonat < 0),
      fn = function(x) paste(x,md("\\textcolor{green}{\\FilledSmallTriangleDown}"))
  )  %>% 
  cols_label(
    time = md("**Stand**"),
    value = md("**Wert**"), 
    delta_vormonat = md("**Delta (Vormonat)**")
  )
```

@@

# hallo

A confidence indicator is a statistical indicator based on the results from business surveys interrogating enterprises on their current economic situation and their expectations about future developments. Five separate confidence indicators are produced, for industry, construction, services, retail trade and consumers.

A confidence indicator is a statistical indicator based on the results from business surveys interrogating enterprises on their current economic situation and their expectations about future developments. Five separate confidence indicators are produced, for industry, construction, services, retail trade and consumers.
A confidence indicator is a statistical indicator based on the results from business surveys interrogating enterprises on their current economic situation and their expectations about future developments. Five separate confidence indicators are produced, for industry, construction, services, retail trade and consumers.

A confidence indicator is a statistical indicator based on the results from business surveys interrogating enterprises on their current economic situation and their expectations about future developments. Five separate confidence indicators are produced, for industry, construction, services, retail trade and consumers.

A confidence indicator is a statistical indicator based on the results from business surveys interrogating enterprises on their current economic situation and their expectations about future developments. Five separate confidence indicators are produced, for industry, construction, services, retail trade and consumers.

```{r plot5, echo=FALSE,  include=FALSE, message=FALSE,warning=FALSE}

rm(list=ls())

tsl <- get_time_series(c(
  "ch.kof.esi.index",
  "eu.ec.esi.eu.esi"))
a1 <- as.data.frame(tsl$ch.kof.esi.index)
a1 <- rename(a1,"ESI-CH"=x)
a2 <- as.data.frame(tsl$eu.ec.esi.eu.esi)
a2 <- rename(a2,"ESI-EU"=x)
#a <-  rbind(a1,a2)
b <- seq(as.Date("2007/4/1"), by = "month", length.out = nrow(a1))
a1 <- relocate(mutate(a1,b),b)
a1 <- rename(a1,"time"=b)

b <- seq(as.Date("1985/1/1"), by = "month", length.out = nrow(a2))
a2 <- relocate(mutate(a2,b),b)
a2 <- rename(a2,"time"=b)

a <- merge(a1,a2,by="time",all=TRUE)

sel <- a %>%
  filter(time >= "2019-01-01"
         #MEASURE == "STE"
  ) |>
  # let's focus on cols location, time value, because none
  # of the other cols contain information, i.e., all their values
  # are the same

  select(time, `ESI-CH`,`ESI-EU`)

sel <- pivot_longer(sel, cols = 2:3, names_to ="Country",
 values_to = "cases")

p <- ggplot(data=sel,
       mapping=aes(x=time,y=cases,
                   color=Country))+
    geom_line(size=.7)+
    scale_color_manual(name="",values = c("#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: KOF", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom") +
    #scale_color_discrete(name="")+
     coord_fixed(ratio=8) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    #scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
    #scale_x_date(date_breaks = "6 month", date_labels ="%m-%Y")+
    scale_x_date(date_labels = "%b %y",breaks=break.vec) +
    theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=12)#, 
  #  face=1)
  ) 
pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/ESI.pdf')
print(p)
dev.off()

# just for viz
tsl <- get_time_series(c(
  "ch.kof.esi.index",
  "eu.ec.esi.eu.esi"))
s_tsl <- lapply(tsl,window, start=c(2010,1))
#pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/ESI.pdf')
#tsplot(s_tsl)
#legend('topleft', legend=c("ESI Schweiz", "ESI EU"), bg='white')
#dev.off()
dates_2 <- date_decimal(as.numeric(time(s_tsl$ch.kof.esi.index)))

```
\begin{figure}[] \centering
\includegraphics[trim={0 0cm 0 0cm },clip,width=.8\textwidth]
{/Users/simonwey/Repos/Foreign_economics/Graphics/ESI.pdf}
\caption{Economic Sentiment Indicator Schweiz und EU} 
\label{Inf_M_W}
\end{figure}

**Monat** | **`r month(dates_2[length(date_decimal(as.numeric(time(s_tsl$ch.kof.esi.index))))-1],label=TRUE,abbr = FALSE)`** | **`r month(dates_2[length(date_decimal(as.numeric(time(s_tsl$ch.kof.esi.index))))],label=TRUE,abbr = FALSE)`**
------------- | -------------|-------------
**ESI Schweiz** | `r round(s_tsl$ch.kof.esi.index[length(s_tsl$ch.kof.esi.index)-1],1)` | `r round(s_tsl$ch.kof.esi.index[length(s_tsl$ch.kof.esi.index)],1)`
------------- | -------------|-------------
**ESI EU** | `r round(s_tsl$eu.ec.esi.eu.esi[length(s_tsl$eu.ec.esi.eu.esi)-1],1)` | `r round(s_tsl$eu.ec.esi.eu.esi[length(s_tsl$eu.ec.esi.eu.esi)],1)`
Table: ESI, letzte Werte. Quelle: KOF

```{r plot0, echo=FALSE,  include=FALSE, message=FALSE,warning=FALSE}

rm(list=ls())

#query <- search_eurostat(pattern="hindering", fixed=FALSE)

cat <- c("AT","DE","EA19","FR","IT")
ty <- c("BS-ESI-I","BS-ICI-BAL","BS-SCI-BAL")  #  ,"BS-ESI-I",
t <- c("BAD","VBAD")#"GOOD","VGOOD")

#dat_hind_fac_i <- get_eurostat(id="ei_bsin_q_r2") #Industry (quarterly: ei_bsin_q_r2)
#dat_hind_fac_s <- get_eurostat(id="ei_bsse_q_r2") #Services (quarterly: ei_bsse_q_r2)
dat_s_indic <- get_eurostat(id="ei_bssi_m_r2") 
#dat_empl_exp <- get_eurostat(id="teibs040")

#d <- filter(dat,indic %in% ty, geo == "IT", s_adj =="SA",time>="2010-01-01") 
d <- filter(dat_s_indic,indic %in% ty, geo %in% cat, s_adj =="SA",time>="2020-01-01")

d$geo[d$geo=="AT"] <- "Österreich"
d$geo[d$geo=="EA19"] <- "EU-19"
d$geo[d$geo=="DE"] <- "Deutschland"
d$geo[d$geo=="FR"] <- "Frankreich"
d$geo[d$geo=="IT"] <- "Italien"

d$indic[d$indic=="BS-ESI-I"] <- "Wirtschaftliche Lage"
d$indic[d$indic=="BS-ICI-BAL"] <- "Industrie: Vertrauensindikator"
d$indic[d$indic=="BS-SCI-BAL"] <- "Dienstleistungen: Vertrauensindikator"

break.vec <- c(seq(from = min(d$time), to = max(d$time),
                   by = "12 month"),max(d$time))

p <- ggplot(data = d) + 
    geom_line(mapping = aes(x = time, y = values, color=indic),size=.6) + 
    scale_color_manual(name="HADK",values = c("#eb4255","#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    coord_fixed(ratio=5) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
    #scale_x_date(date_breaks = "6 month", date_labels ="%m-%Y")+
    scale_x_date(date_labels = "%b %y",breaks=break.vec) +
    theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
  #  face=1)
  ) +
    #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_ESI.pdf')
print(p)
dev.off()

\begin{figure}[h] \centering
\includegraphics[trim={0 0cm 0 0cm },clip,width=\textwidth]{/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_ESI.pdf}
\caption{Einschätzungen zur wirtschaftlichen Lage in der Gesamtwirtschaft und den Sektoren} 
\label{Inf_M_W}
\end{figure}

```{r}
# Fake confusion matrix to work with
x = structure(c(34L, 6L, 9L, 35L), .Dim = c(2L, 2L), .Dimnames = structure(list(
    Actual = c("EU-19","Deutschland" ), Predicted = c(format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[2],"%B"), format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[1],"%B"))), .Names = c("Land", 
"Einschätzung zur Wirtschaft")), class = "table")

x=cbind(x, prop.table(x), prop.table(x, 1), prop.table(x,2))
x[, -c(1,2)] = sapply(x[,-c(1,2)], function(i) paste0(sprintf("%1.1f", i*100),"%"))
x = cbind(Actual=rownames(x), x)
```

**Wirtsch. Lage** | **`r format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[2],"%B")`** | **`r format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[1],"%B")`**
------------- | -------------|-------------
**EU-19** | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$values[2]` | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$values[1]`
**Deutschland** | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Deutschland")$values[2]` | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Deutschland")$values[1]`
**Frankreich** | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Frankreich")$values[2]` | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Frankreich")$values[1]`
**Italien** | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Italien")$values[2]` | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Italien")$values[1]`
**Österreich** | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Österreich")$values[2]` | `r filter(d,indic=="Wirtschaftliche Lage" & geo=="Österreich")$values[1]`
Table: Einschätzung zur wirtschaftlichen Lage in den entsprechenden Ländern. Quelle: Eurostat

```{r}
x <- structure(c(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$values[2], filter(d,indic=="Wirtschaftliche Lage" & geo=="Deutschland")$values[2], filter(d,indic=="Wirtschaftliche Lage" & geo=="Frankreich")$values[2], filter(d,indic=="Wirtschaftliche Lage" & geo=="Italien")$values[2],filter(d,indic=="Wirtschaftliche Lage" & geo=="Österreich")$values[2],filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$values[1], filter(d,indic=="Wirtschaftliche Lage" & geo=="Deutschland")$values[1], filter(d,indic=="Wirtschaftliche Lage" & geo=="Frankreich")$values[1], filter(d,indic=="Wirtschaftliche Lage" & geo=="Italien")$values[1],filter(d,indic=="Wirtschaftliche Lage" & geo=="Österreich")$values[1],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="EU-19")$values[2],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Deutschland")$values[2],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Frankreich")$values[2],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Italien")$values[2],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Österreich")$values[2],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="EU-19")$values[1],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Deutschland")$values[1],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Frankreich")$values[1],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Italien")$values[1],filter(d,indic=="Industrie: Vertrauensindikator" & geo=="Österreich")$values[1],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="EU-19")$values[2],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Deutschland")$values[2],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Frankreich")$values[2],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Italien")$values[2],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Österreich")$values[2],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="EU-19")$values[1],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Deutschland")$values[1],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Frankreich")$values[1],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Italien")$values[1],filter(d,indic=="Dienstleistungen: Vertrauensindikator" & geo=="Österreich")$values[1]),.Dim = c(5, 6), .Dimnames = structure(list(Actual = c("EU-19", "Deutschland","Frankreich","Italien","Österreich"), Predicted = c( format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[2],"%B"), format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[1],"%B"),format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[2],"%B"), format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[1],"%B"),format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[2],"%B"), format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[1],"%B"))), .Names = c("Actual", "Predicted")), class = "table")

PrintConfusionMatrix <- function(data, ...) {

  stopifnot(all(dim(x) == c(5, 6)))

#  colnames(x) <- sprintf("\\emph{%s}", colnames(x)) # highlight colnames
#  rownames(x) <- sprintf("\\emph{%s}", rownames(x)) # highlight rownames

  cat('\\begin{tabular}{|c *{8}{|c{2cm}}|} \\cline{2-7}
    \\multicolumn{1}{c|}{} & \\multicolumn{6}{c|}{\\textbf{Einschätzungen}} \\\\ \\cline{2-7}
    \\multicolumn{1}{c|}{} & \\multicolumn{2}{c|}{\\textbf{Wirtsch. Lage}} & \\multicolumn{2}{c|}{\\textbf{Ind.\nVertrauensind.}} & \\multicolumn{2}{c|}{\\textbf{DL\n Vertrauensind.}} \\\\ \\hline
    \\textbf{Land} ')

  print(xtable(x),
        only.contents = TRUE, 
        comment = FALSE,
        sanitize.colnames.function = identity, 
        sanitize.rownames.function = identity, 
        hline.after = 0:5,
        ...)
  cat("\\end{tabular}")
}
```

```{r, results='asis'}
PrintConfusionMatrix(x)
```

```{r}
  x <- structure(c(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$values[2], filter(d,indic=="Wirtschaftliche Lage" & geo=="Deutschland")$values[2], filter(d,indic=="Wirtschaftliche Lage" & geo=="Frankreich")$values[2], filter(d,indic=="Wirtschaftliche Lage" & geo=="Italien")$values[2],filter(d,indic=="Wirtschaftliche Lage" & geo=="Österreich")$values[2],filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$values[1],filter(d,indic=="Wirtschaftliche Lage" & geo=="Deutschland")$values[1],filter(d,indic=="Wirtschaftliche Lage" & geo=="Frankreich")$values[1],filter(d,indic=="Wirtschaftliche Lage" & geo=="Italien")$values[1],filter(d,indic=="Wirtschaftliche Lage" & geo=="Österreich")$values[1]),.Dim = c(5, 2), .Dimnames = structure(list(Actual = c("EU-19", "Deutschland","Frankreich","Italien","Österreich"), Predicted = c( format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[2],"%B"),  format(filter(d,indic=="Wirtschaftliche Lage" & geo=="EU-19")$time[1],"%B"))), .Names = c("Actual", "Predicted")), class = "table")

PrintConfusionMatrix <- function(data, ...) {

  stopifnot(all(dim(x) == c(5, 2)))

#  colnames(x) <- sprintf("\\emph{%s}", colnames(x)) # highlight colnames
#  rownames(x) <- sprintf("\\emph{%s}", rownames(x)) # highlight rownames

  cat('\\begin{tabular}{|c *{8}{|c{2cm}}|} \\cline{2-3}
    \\multicolumn{1}{c|}{} & \\multicolumn{2}{c|}{\\textbf{Wirtsch. Lage}} \\\\ \\hline     \\textbf{Land} ')

  print(xtable(x),
        only.contents = TRUE, 
        comment = FALSE,
        sanitize.colnames.function = identity, 
        sanitize.rownames.function = identity, 
        hline.after = 0:5,
        ...)
  cat("\\end{tabular}")
}
```

```{r, results='asis'}
PrintConfusionMatrix(x)
```

## Industrie

```{r plot1, echo=FALSE,  include=FALSE, message=FALSE,warning=FALSE}

rm(list=ls())

cat <- c("AT","DE","EA19","FR","IT")
t <- c("BS-FLP3-PC","BS-FLP5-PC","BS-FLP1-PC")  #  ,"BS-ESI-I",

dat_hind_fac_i <- get_eurostat(id="ei_bsin_q_r2") #Industry (quarterly: ei_bsin_q_r2)
#dat_hind_fac_s <- get_eurostat(id="ei_bsse_q_r2") #Services (quarterly: ei_bsse_q_r2)
#dat_s_indic <- get_eurostat(id="ei_bssi_m_r2") 
#dat_empl_exp <- get_eurostat(id="teibs040")

#d <- filter(dat,indic %in% ty, geo == "IT", s_adj =="SA",time>="2010-01-01") 
d_hind_i <- filter(dat_hind_fac_i,indic ==  "BS-FLP3-PC", geo %in% cat, s_adj == "SA",time>="2016-01-01")

d_hind_i$time <- as.yearqtr(d_hind_i$time)

d_hind_i$geo[d_hind_i$geo=="AT"] <- "Österreich"
d_hind_i$geo[d_hind_i$geo=="EA19"] <- "EU-19"
d_hind_i$geo[d_hind_i$geo=="DE"] <- "Deutschland"
d_hind_i$geo[d_hind_i$geo=="FR"] <- "Frankreich"
d_hind_i$geo[d_hind_i$geo=="IT"] <- "Italien"

d_hind_i$indic[d_hind_i$indic=="BS-FLP3-PC"] <- "Arbeitskräftemangel"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP5-PC"] <- "Andere"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP1-PC"] <- "Keine"
#d_hind_i$indic[d_hind_i$indic=="BS-FLP2-PC"] <- "Insufficient Demand"

#break.vec <- c(seq(from = min(d_hind_i$time), to = max(d_hind_i$time),
#                   by = "16 month"),max(d_hind_i$time))

p <- ggplot(data = d_hind_i) + 
    geom_line(mapping = aes(x = time, y = values, color=indic),size=.6) + 
    scale_color_manual(values = c("#eb4255","#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=20) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
  #scale_x_date(date_labels = "%b %y",breaks=break.vec) +
    zoo::scale_x_yearqtr(breaks = seq(from = min(d_hind_i$time), to = max(d_hind_i$time), by = 2),format = '%Y Q%q')+
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +
     #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hin_i.pdf')
print(p)
dev.off()

```
\begin{figure}[h] \centering
\includegraphics[trim={0 2.5cm 0 0cm },clip,width=\textwidth]{/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hin_i.pdf}
\caption{Industrie: Hemmnisse in der Produktion} 
\label{Inf_M_W}
\end{figure}

```{r}
x <- structure(c(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="Österreich")$values[1],filter(d_hind_i,indic=="Keine" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Keine" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Keine" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Keine" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Keine" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Keine" & geo=="Österreich")$values[1],filter(d_hind_i,indic=="Andere" & geo=="EU-19")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Deutschland")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Frankreich")$values[2], filter(d_hind_i,indic=="Andere" & geo=="Italien")$values[2],filter(d_hind_i,indic=="Andere" & geo=="Österreich")$values[2],filter(d_hind_i,indic=="Andere" & geo=="EU-19")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Deutschland")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Frankreich")$values[1], filter(d_hind_i,indic=="Andere" & geo=="Italien")$values[1],filter(d_hind_i,indic=="Andere" & geo=="Österreich")$values[1]),.Dim = c(5, 6), .Dimnames = structure(list(Actual = c("EU-19", "Deutschland","Frankreich","Italien","Österreich"), Predicted = c(format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[2],"%YQ%q"),format(filter(d_hind_i,indic=="Arbeitskräftemangel" & geo=="EU-19")$time[1],"%YQ%q"))), .Names = c("Actual", "Predicted")), class = "table")

PrintConfusionMatrix <- function(data, ...) {

  stopifnot(all(dim(x) == c(5, 6)))

#  colnames(x) <- sprintf("\\emph{%s}", colnames(x)) # highlight colnames
#  rownames(x) <- sprintf("\\emph{%s}", rownames(x)) # highlight rownames

  cat('\\begin{tabular}{|c *{8}{|c{2cm}}|} \\cline{2-7}
    \\multicolumn{1}{c|}{} & \\multicolumn{6}{c|}{\\textbf{Einschätzungen Hemmnisse}} \\\\ \\cline{2-7}
    \\multicolumn{1}{c|}{} & \\multicolumn{2}{c|}{\\textbf{Arbeitskräftemangel}} & \\multicolumn{2}{c|}{\\textbf{Keine}} & \\multicolumn{2}{c|}{\\textbf{Andere}} \\\\ \\hline
    \\textbf{Land} ')

  print(xtable(x),
        only.contents = TRUE, 
        comment = FALSE,
        sanitize.colnames.function = identity, 
        sanitize.rownames.function = identity, 
        hline.after = 0:5,
        ...)
  cat("\\end{tabular}")
}
```

```{r, results='asis'}
PrintConfusionMatrix(x)
```

## Dienstleistungen

```{r plot2, echo=FALSE,  include=FALSE, message=FALSE,warning=FALSE}

rm(list=ls())

cat <- c("AT","DE","EA19","FR","IT")
t <- c("BS-FLB3-PC","BS-FLB6-PC","BS-FLB1-PC")  #  ,"BS-ESI-I",

dat_hind_fac_s <- get_eurostat(id="ei_bsse_q_r2") #Industry (quarterly: ei_bsin_q_r2)

d_hind_s <- filter(dat_hind_fac_s,indic =="BS-FLB3-PC", geo %in% cat, s_adj == "SA",time>="2019-01-01")

d_hind_s$time <- as.yearqtr(d_hind_s$time)

#d_hind_s$time <- paste(format(d_hind_s$time, "%Y"),  # Convert dates to quarterly
#                            sprintf("%i", (as.POSIXlt(d_hind_s$time)$mon) %/% 3L + 1L), 
#                            sep = "-Q")

#sprintf("%i", (as.POSIXlt(d_hind_s$time %m-% months(1))$mon) %/% 3L + 1L),

d_hind_s$geo[d_hind_s$geo=="AT"] <- "Österreich"
d_hind_s$geo[d_hind_s$geo=="EA19"] <- "EU-19"
d_hind_s$geo[d_hind_s$geo=="DE"] <- "Deutschland"
d_hind_s$geo[d_hind_s$geo=="FR"] <- "Frankreich"
d_hind_s$geo[d_hind_s$geo=="IT"] <- "Italien"

d_hind_s$indic[d_hind_s$indic=="BS-FLB3-PC"] <- "Arbeitskräftemangel"
#d_hind_s$indic[d_hind_s$indic=="BS-FLB6-PC"] <- "Andere"
#d_hind_s$indic[d_hind_s$indic=="BS-FLB1-PC"] <- "Keine"

#d_hind_s$indic[d_hind_s$indic=="BS-FLB2-PC"] <- "Insufficient Demand"

break.vec <- c(seq(from = as.Date(as.yearqtr(min(d_hind_s$time))), to = as.Date(as.yearqtr(max(d_hind_s$time))),
                   by = "quarter"),as.Date(as.yearqtr(max(d_hind_s$time))))

p <- ggplot(data = d_hind_s) + 
    geom_line(mapping = aes(x = time, y = values, color=indic),size=.6) + 
    scale_color_manual(values = c("#eb4255","#8E44AD","#ffa500","#659065","#A0522D")) +
    #  geom_text(data=dat %>% group_by(geo)%>% filter(time==max(time)),size=2.6) + 
    # theme(legend.position="left")+
    #  scale_color_manual(values = c("#8E44AD", "#F1C40F","#34495E","#138D75","#E74C3C","#F8C471"))+
    labs(caption="Quelle: Eurostat", #title = "Erwerbslosenrate",
      #subtitle = "Quelle: Eurostat",
      y = "",
      x = "") +
    theme_minimal()+
    theme(legend.position="bottom",legend.title=element_blank()) + 
    #guides(color = guide_legend(nrow = 2, byrow = TRUE)) +
    #coord_fixed(ratio=.2) +  
    #ggtitle("Inflationsraten - excluding energy")+
    theme(text = element_text(size = 15))+
    scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
 # scale_x_date(date_labels = "%YQ%q",breaks=break.vec) +
 # zoo::scale_x_yearqtr(limits = c(min(d_hind_s$time), max(d_hind_s$time)),format = '%Y Q%q')+
  zoo::scale_x_yearqtr(breaks = seq(from = min(d_hind_s$time), to = max(d_hind_s$time), by = 2),format = '%Y Q%q')+
  #scale_x_yearqtr(format = "%YQ%q",breaks=break.vec )+
  theme(axis.text.x = element_text( 
    angle = 60, 
    #color="blue", 
    vjust=0.6,
    size=10)#, 
    #  face=1)
  ) +    #facet_wrap(~ LOCATION, nrow = 2) 
    facet_wrap(factor(geo,levels=c("EU-19","Deutschland","Frankreich","Italien","Österreich")) ~ .,nrow=2) #+
    #geom_text_repel(
    #aes(x=Time,y = values,label=values), data = data_ends,
    #fontface ="plain", color = "black", size = 5
 # )

pdf('/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hin_s.pdf')
print(p)
dev.off()

\begin{figure}[] \centering
\includegraphics[trim={0 2.5cm 0 0cm },clip,width=\textwidth]
{/Users/simonwey/Repos/Foreign_economics/Graphics/wrap_Hin_s.pdf}
\caption{Dienstleistungen: Hemmnisse beim Erbringen von Dienstleistungen} 
\label{Inf_M_W}
\end{figure}

>>>>

KOF_Baro_table %>% 
  gt(caption = "") %>%
  tab_header(title = md("KOF-Bartmeter. *Quelle:* KOF"),
             subtitle = "") %>% 
  fmt_date(
    columns = time,
    date_style = "month"
  ) %>% 
  fmt_number(
    columns = c(value, delta_vormonat),
    decimals = 1
  ) %>%
  cols_align(
    align = "left",
    columns = time
  ) %>% 
 text_transform(
    locations = cells_body(
      columns = delta_vormonat,
      rows = delta_vormonat > 0),
    fn = function(x) paste(x, md("\\textcolor{green}{\\FilledSmallTriangleUp}"))
  ) %>%
  text_transform(
    locations = cells_body(
      columns = delta_vormonat,
      rows = delta_vormonat < 0),
      fn = function(x) paste(x,md("\\textcolor{red}{\\FilledSmallTriangleDown}"))
  )  %>% 
  cols_label(
    time = md("**Stand**"),
    value = md("**Wert**"), 
    delta_vormonat = md("**Delta (Vormonat)**")
  )
```

@@
